Modular Model-Checking for Fault-Tolerant Distributed System Implementations

### 2016-11-28 doc/om-paper/paper.tex
Minor edits on the abstract

\begin{abstract}
With proof techniques like IC3 and $k$-induction with user-supplied invariants, model-checking scales further than ever before. Still, fault-tolerant distributed systems are particularly challenging to model-check given their large state space and non-determinism. The typical approach to controlling complexity is to construct ad-hoc abstractions of faults, message-passing, and behavior to simplify their behavior. However, these abstractions come at the price of divorcing the model from its implementation and making refactoring difficult. In this work, we present a systematic model for fault-tolerant distributed system verification that combines calendar automata, synchronous observers, and abstract state machines specialized for model-checking. We demonstrate the efficacy of the framework by presenting the first model-checked \emph{implementation} of the Hybrid Oral Messages algorithm, using a fast majority vote, then demonstrate how modifications along axes such as the fault model, topology, node behavior, and require only local modifications to the model and proofs.
\end{abstract}

>>>>

\begin{abstract}
With proof techniques like IC3 and $k$-induction with user-supplied
invariants, model-checking scales further than ever before.  Still,
fault-tolerant distributed systems are particularly challenging to
model-check given their large state space and non-determinism. The
typical approach to controlling complexity is to construct ad-hoc
abstractions of faults, message-passing, and behaviors.  However,
these abstractions come at the price of divorcing the model from its
implementation and make refactoring difficult. In this work, we
present a systematic model for fault-tolerant distributed system
verification that combines calendar automata, synchronous observers,
and abstract state machines specialized for model-checking. We
demonstrate the efficacy of the framework by presenting the first
model-checked \emph{implementation} of the Hybrid Oral Messages
algorithm, using a fast majority vote, then demonstrate how
modifications along axes such as the fault model, topology, and node
behavior require only local modifications to the model and proofs.
\end{abstract}
